---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)

desc = read.dcf("DESCRIPTION")
desc = setNames(as.list(desc), colnames(desc))
```

# `r desc$Package`

<!-- badges: start -->
<!-- badges: end -->

## Package overview

Title: ***`r desc$Title`***

This package serves as a bridge to `{tidymodels}`, allowing you to manifest `{tidymodels}` API and PerpetualBooster at the same time. 

## Installation

Install ``r paste0("{", desc$Package, "}")`` on R-universe

``` r
install.packages("perpsnip", repos = "https://joshuamarie.r-universe.dev")
```

You can install the development version of perpsnip from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("joshuamarie/perpsnip")
```

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)

desc = read.dcf("DESCRIPTION")
desc = setNames(as.list(desc), colnames(desc))
```

# `r desc$Package`

<!-- badges: start -->
[![R-CMD-check](https://github.com/joshuamarie/perpsnip/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/joshuamarie/perpsnip/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`r desc$Description`

## Installation

Install from R-universe:

```r
install.packages("perpsnip", repos = "https://joshuamarie.r-universe.dev")
```

Or the development version from GitHub:

```r
# install.packages("pak")
pak::pak("joshuamarie/perpsnip")
```

## Usage

PerpetualBooster handles both classification and regression task. 

### Classification with iris

```{r}
perpsnip::perpsnip(mode = "classification", budget = 0.5) |>
    parsnip::fit(Species ~ ., data = iris) |>
    parsnip::augment(new_data = iris) |>
    yardstick::metrics(truth = Species, estimate = .pred_class)
```

### Regression with mtcars

```{r}
perpetual::perpsnip(mode = "regression", budget = 1) |>
    parsnip::fit(mpg ~ cyl + . - vs - am, data = mtcars) |>
    parsnip::augment(new_data = mtcars) |>
    yardstick::metrics(truth = mpg, estimate = .pred)
```

## Related

- [`{perpetual}`](https://github.com/perpetual-ml/perpetual) — the underlying PerpetualBooster engine
- [`{parsnip}`](https://parsnip.tidymodels.org) — the modeling API this package extends
